upwell_IDX

### 2019-08-09 upwell_IDX.Rmd
update

```{r}
ggplot(data = SACTN_MCS_clims, aes(x = t, y = temp)) +
  geom_line() +
  geom_point(data = filter(SACTN_MCS_clims, event == TRUE), colour = "navy") +
  geom_rug(data = filter(index, ui.saws == TRUE), sides = "b") +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~site, ncol = 1) +
  theme_grey() +
  labs(y = "Temperature (°C)", x = NULL)
```

>>>>

```{r}
match_func <- function(df){
  match <- SACTN_MCS_clims  %>% 
  left_join(df, by = c("site", "t")) %>% 
  na.trim()
  return(match)
}

index <- index %>% 
  dplyr::rename(site = sites) %>% 
  dplyr::rename(t = date)

match <- match_func(df = index)

upwell_MCS <- ggplot(data = match, aes(x = t, y = temp)) +
  geom_line() +
  geom_point(data = filter(match, event == TRUE), colour = "navy") +
  geom_rug(data = filter(match, ui.saws == TRUE), sides = "b") +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~site, ncol = 1) +
  theme_grey() +
  labs(y = "Temperature (°C)", x = NULL)
upwell_MCS
```
